### 2016-11-16 thesis/intro/intro.tex
finally finished the obesity section of intro

\noindent
As more of the younger generation is gaining weight and becoming obese, having the risks and disease burden associated with obesity at such early age are not ideal -- both economically and epidemiologically -- and poses a threat to the growing population that are becoming more obese.

@@

\citep{Malik2013}

>>>>

\noindent
As more of the younger generation is gaining weight and becoming obese, having the risks and disease burden associated with obesity at such early age are not ideal (both economically and epidemiologically) and poses a threat to the growing population that are becoming more obese.

@@

It is apparent from previous sections that obesity has become a serious problem that the world needs to prioritise to solve immediately.
Even though obesity has been regarded as one of the many global problems to solve, the progress has been slow.

\citet{Sacks2009} proposed an \gls{opa} framework that was based on the framework developed by \citet{WHO2006}.
In this framework, \citet{Sacks2009} have added extra features so that the policies were targeted to impact three levels of the underlying environment of obesity: the socio-ecological environment (upstream), lifestyle/behavioural changes (midstream), and health services support (downstream).

The upstream approach targets the underlying economic, social and physical norms that the population is currently in.
By targeting the broad socioeconomic environment that the population lives in, such as taxation, education, employment and housing \citep{Sacks2009}.
In doing so, it is possible to have a significant change in the population behaviours and eventually improve the health outcomes of the population.

The midstream approach targets the population or subpopulation behaviour change to improve the eating and physical activity behaviours in these groups.
Unlike in the upstream approach, the midstream approach aims to change the behaviour by implementing social marketing and programmes that encourage such changes \citet{Sacks2009}.
Again, the result of this approach will be an improvement in the overall positive behaviour of the population towards healthy eating and physical activity.

The downstream approach targets to support the health services and clinical interventions.
Unlike upstream and midstream approaches, downstream approach generally acts on an individual level, whereby the focus is on the management of the health of an individual and/or the individual's family \citet{Sacks2009}.
Although not as efficient as upstream or midstream approaches, downstream approach will help improve the habits and behaviours to promote weight management.\\

\noindent
In the recent years, obesity has been declared as a global priority \citep{Malik2013}.
Furthermore, comprehensive global monitoring framework, multi-sectoral actions and strengthening of the national policies have been implemented to better control the obesity epidemic \citep{Malik2013}.
In many countries, the nutritional labelling on products have been adjusted to include the ingredients that have negative impact on obesity (for example, \textit{trans} fat), and even reduce or remove these ingredients from food \citep{Malik2013}.

Food marketing can also be a problem in a highly competitive society that we live in.
To sell their products that are high in fat, sugar and portion size, food industries market and advertise their products to the population, especially young children, in order to stay ahead in their market place \citep{Chan2010, Malik2013}.
Even though there is a strong evidence of food marketing influencing the eating behaviours and food preferences in children, very few countries have been able to reduce these marketing and advertising strategies of unhealthy food \citep{Hawkes2007a, Malik2013}.

In contrast to these upstream/midstream approaches, there are some clinical interventions and treatments that help manage weight in an individual.
One of these therapies is bariatric surgery for obese patients, especially morbidly obese patients \citep{Buchwald2004}.
Through their meta-analysis, \citet{Buchwald2004} showed that bariatric surgery was able to reduce many of the the comorbidities associated with obesity.
The fact that these improvements and complete resolution of the comorbidities in high proportion of patients that underwent bariatric surgery shows that, even though it acts on an individual level, downstream approaches such as bariatric surgery may be a highly effective, but not an efficient, method of preventing obesity in the population.\\

\noindent
It is evident that the most efficient way to reduce the proportion of the population that are obese is to implement national policies that affect the upstream or midstream factors.
These policies, although they are efficient at targeting the underlying problem, may take a long time to make a significant effect.
On the otherhand, individual therapeutic plans that affect the downstream factors may be very effective in achieving the desired goal of weight loss, but it is very resource intensive and upscaling this approach would be practically impossible.

The management of obesity at an early stage with midstream and/or downstream approaches while the upstream approach takes effect would be the key to success in controlling for the global obesity epidemic.
